Rutgers Autonomous Aircraft Team\\Technical Report\\2010 AUVSI UAS Competition

### 2010-05-22 paper/paper.tex
added figure of knight two, finished 12ft telemaster

\documentclass[10pt]{report}
\usepackage[pdftex]{graphicx}
\usepackage{hyperref}
\hypersetup{ colorlinks=true
           , linkcolor=cyan
           , pdfnewwindow=true 
           }
\usepackage{amsmath}
\usepackage{subfig}
\usepackage{listings}
\usepackage{float}
\usepackage{textcomp}
\usepackage{multicol}
\newcommand{\HRule}{\rule{\linewidth}{0.5mm}}
\hyphenation{auto-nomous}

@@

Figure goes here: Photos of Knight Two in construction

>>>>

\documentclass[10pt]{report}
\usepackage[pdftex]{graphicx}
\usepackage{hyperref}
\hypersetup{ colorlinks=true
           , linkcolor=cyan
           , pdfnewwindow=true 
           }
\usepackage{amsmath}
\usepackage{subfig}
\usepackage{listings}
\usepackage{float}
\usepackage{textcomp}
\usepackage{multicol}
\newcommand{\HRule}{\rule{\linewidth}{0.5mm}}
\hyphenation{auto-nomous construction}

@@

\begin{figure}
	\centering
	\subfloat[The unfinished \emph{Knight Two}]{\label{fig:knighttwo_construction} 
			\includegraphics[width=0.4\textwidth]{../images/knighttwo_underconstruction.jpg}}
	\subfloat[A completed 12 Foot Telemaster. Photo Credit: Hobby Lobby] {\label{fig:knighttwo_12ft_telemaster} 
			\includegraphics[width=0.4\textwidth]{../images/telemaster_12ft_hobbylobby.jpg}}
  	\label{fig:knighttwo}
  	\caption[Knight Two]{Knight Two}
\end{figure}
Someone please detail the outer dimensions. The inner dimensions, space used for flight electronics, space used for payload underneath. Landing gear height. Number of servos and their locations
